---
title: "Analysis of the Pima Native American Cohort"
author: "Parth Jariwala"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(gtsummary)
library(ggplot2)
library(here)
library(gt)
```

# Introduction
This data set is on a Pima Native American cohort and was from the 
National Institute of Diabetes and Digestive and Kidney Disease. 
This data set includes several medical predictor variables and one outcome 
variable, whether the person has diabetes or not. Variables include, number 
of pregnancies, glucose level, BMI, age, diastolic blood pressure, and a few 
more. For my R markdown report I will look to see the distribution of the 
glucose levels across the cohort and which variables have an association with 
the outcome (Diabetes diagnosis).

# Descriptive Statistics
In Table 1, the key variables in the data set are summarized and 
stratified whether the participant has a diabetes diagnosis or not 

```{r, desc-stats, echo=FALSE}
table_one <- readRDS(
	here::here("output/table_one.rds"))

table_one
```


```{r, fig-one, echo=FALSE}
#| fig.cap = "Figure 1. Disribution of Glucose Levels"
figure1 <- readRDS(
	here::here("output/figure_1.rds")
)

figure1
```
A histogram was created to display the distribution of glucose levels
across the cohort.


# Results and Analysis
```{r, data-analysis, echo=FALSE}

table2 <- readRDS(
	here::here("output/log_regr_summary.rds")
)

table2
```
Table 2. A logistic regression model was ran to find an association between each of the 
predictor variables and the diabetes diagnosis outcome. 
